No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-07 R/MSE manuscript.Rmd
Fix names of fields taken from Rdata; edit climate change text box

mgmt.join<-mgmt %>% 
  group_by(fkStudyID) %>%
  summarise(ManagementType = toString(sort(unique(ManagementType))),
            AlternativesEvaluated = toString(sort(unique(AlternativesEvaluated))))

@@

We review published MSEs including climate change as a driver against the stages in a SDM process to:  Highlight unique aspects of MSEs that model climate change as a driver to help inform fisheries management

We filtered the original set of MSE by searching for the term "climate change" within the set. We found that, as of the end of December 2018, 11 MSEs included climate change as a driver. We reviewed the climate change MSEs using the same methodology described above. These MSEs have been concentrated in North America and Australia (Figure \@ref(fig:mapfigure)).

>>>>

mgmt.join<-mgmt %>% 
  group_by(fkStudyID) %>%
  summarise(ManagementType = toString(sort(unique(MPManagementTool))),
            AlternativesEvaluated = toString(sort(unique(MPAlternativesEvaluated))))

@@

We review published MSEs including climate change as a driver against the stages in a SDM process to highlight unique aspects of MSEs that model climate change as a driver to help inform fisheries management

We filtered the original set of MSE by searching for the term "climate change" within the set, reviewing 16 published MSEs included climate change as a driver as of December 31st, 2019. We reviewed the climate change MSEs using the same methodology described above. These MSEs have been concentrated in North America and Australia (Figure \@ref(fig:mapfigure)).
